{\LARGE Basis Choice for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-08 Paper/main.tex
Rewriting Interpretation, correcting things, starting application interpretation for basis expansion

	\subsection{Results}	
	The discussed results and figures of $\hat{\beta}(t)$ for the simulation can be found in the appendix. 
	\subsubsection{Basis Expansion Regression}
	The following results origin from the \hyperref[basis_exp_transf]{Estimation using Basis-Representation}, in which we transform the smooth curves to perform regression of a scalar on a finite sequence of regressors, which is then tractable with typical multivariate regression theory. examining the results, it appears that the cross-validated MSPE inherets a convex nature in the increasing basis functions.

	\paragraph{Monomial Basis}
	Due to the in the number of basis functions increasing collinearity of these basis functions, simulations were conducted up until the sixth monomial basis, which already shows signs of numerical instability. This could be solved using orthogonal polynomials like Legendre polynomials, see \cite{Dattoli_2001}. For reasons outlined in {\color{green} Link chapter}, they seem suited for $f_1$. The monomial basis shows a better performance than B-splines for this coefficient function. A hypothesis for this could be that $f_1$ is an entire function, which can be well approximated with a power series. In case of $f_2$, this basis shows the weakest performance out of all basis, which is visible in figure 9 and 10, where it seems like $\hat{\beta}$ is not changing in the amount of noise and shows exaggerated behaviour at the boundaries. This weakness is especially pronounced in the setup $f_2,Y_1$; for the high noise setup, $f_2,Y_2$ this weakness is still visible, but less pronounced. For $f_1$, the simulation selects 5(3) and for $f_2$ 5(5) monomial basis functions for the high(low) signal-to-noise ratios. 
	\vspace{-0.2cm}

	\paragraph{B-spline Basis}
	Simulations with B-spline basis functions were possible from 4 to 18, since from 18 onwards the simulations were running into collinearity problems.
	The smooth function $f_1$ requires only 5(4) B-spline basis functions, for the high(low) signal-to-noise ratio to obtain the best fit for the B-spline basis, which performs the worst for $f_1$. An explanation might be its exaggerated behaviour at the boundaries and the exaggeration of the peculiarities of $f_1$ (figure 7 and 8), which is especially pronounced for the higher noise responses. For $f_2$, 11(6) B-spline basis functions are chosen for the high(low) signal-to-noise ratios. For $f_2$, the B-spline basis functions outperform the monomial basis but come second to the Fourier basis. While the basis seems to recognize the peculiarities in $f_2,Y_1$, it seems to struggle with it for the noisy responses in $f_2,Y_2$ (figure 9 and 10).
	\vspace{-0.2cm}

	\paragraph{Fourier Basis}
	For $f_1$, the simulation chooses a smaller number of Fourier basis functions, 5(3) and a higher number for $f_2$, 9(7) for the setup with the high(low) signal-to-noise ratio. With the low signal-to-noise ratio, the simulation chooses a smaller number of basis functions, which could be to account for the higher noise in the response variable. The Fourier basis functions perform the best for each setup for the basis expansion regression. Several reasons could contribute to this: First, especially $f_1$ shows similar curvature order across the domain while the curvature of $f_2$, while changing, does not display any erratic jumps. Second, both functions feature periodic behavior. Third, $f_2$ does have the same value at the start- and the end of the interval.	\\

	\subsubsection{Functional Principal Component Regression}
		The model which is used for the FPCR is described in \hyperref[fpc_exp_transf]{Estimation using Functional Principal Components}. Additionally to the selection of the truncation parameter $K$, the choice of the number of FPC's adds to the complexity of the model since the approximated eigenvalues and -functions from the decomposition are influenced by the choice of $K$ that was used to approximate the function. But since the FPCR is ultimately estimated with a linear model with the FPC's as regressors, the degrees of freedom in the estimation of the ultimate model are not affected by $K$, but only by the number of FPC's $n_{FPC} \in \{2, 3, 4 \}$. As will be described, it seems that neither a convex behavior of the MSPE, nor a clear relationship can be observed between the increasing number of basis function and the number of FPC's.

	\paragraph{Monomial Basis}
	For $f_1$, the cross-validated MSE is decreasing in the increasing number of FPC's and chosen basis functions for both the setup with the high, and the low signal-to-noise ratio (4,5,6 basis functions for $n_{FPC} \in \{2, 3, 4 \}$). In the setup using $f_2$ we also observe a decreasing MSE in the number of FPC, but a different behavior of the chosen basis functions: While the model selects 10 basis functions for $f_2,Y_1$ and $f_2,Y_2$ using 2 FPC, it only selects 6 for the same two specifications using 3 FPC and 8 for $f_2,Y_1$ and $f_2,Y_2$ with 4 FPC. This might be surprising, since one might assume that the number of basis functions is increasing in $n_{FPC}$ since more basis functions led to less smoothing and therefore more variability in the expanded curves that might be exploited by the FPC's. The monomial basis shows the weakest performance for all three basis functions in each setting.
	\vspace{-0.2cm}

	\paragraph{B-spline Basis}
	For $f_1,Y_1$, the CV suggests a better model with a higher number of FPC's. While the number of basis functions stays at five for two and three used FPC, it increases to six basis functions for $nharm$ = 4. In $f_1,Y_1$, the cross-validated MSE is only slightly affected by $n_{FPC}$, but lowest for $n_{FPC}$ = 3, indicating the possibility of over-fitting for $n_{FPC}$ = 4. $f_2,Y_1$ shows a decrease of MSE in increasing $n_{FPC}$. The same holds true in the setup with $f_2$ and the high signal-to-noise ratio with the decrease being similar in absolute terms. Similar to the two setups with $f_1$, the cross-validated number of basis functions for $f_2$ is increasing in the number of FPC's (4,6,8 for $n_{FPC} \in \{2, 3, 4 \}$)
	\vspace{-0.2cm}

	\paragraph{Fourier Basis}
	We observe similar behaviour as for the FPCR using B-splines. In $f_1,Y_1$, the MSE is decreasing in $n_{FPC}$ while the results in $f_1,Y_2$ might indicate overfitting when using four FPC's. Since it is not possible to calculate the cross-validated MSE for three basis functions for $n_{FPC}$ = 4, the increasing number of basis functions as seen in the FPCR with B-splines can not be observed here for sure. $f_2,Y_1$ displays the greatest relative decline of MSE in the increasing number of FPC's, but in absolute values, therefore acknowledging the higher noise responses for $f_2,Y2$, the decline if MSE is similar to the decline observed for $f_2,Y_2$. Both configurations of $f_2$ are using 5,15,7 basis functions for $n_{FPC} \in \{2, 3, 4 \}$: This behaviour in increasing $n_{FPC}$ opposes the previously reported behaviour of the monomial basis and the increasing nature of the B-splines basis functions.
	\vspace{-0.2cm}

	\subsubsection{Interpretation and Relevance for Application}
	A possible explanation applicable for all setups using Basis Expansion Regression might be the effect of the Bias-Variance tradeoff and the following hypothesis: For the function $f_1$ it might be that little bias is introduced when choosing a small number of basis functions. For $f_2$, a higher number of basis functions is needed, resulting from the inherent peculiarities of $f_2$. This results in higher numbers of basis functions since the amount of bias is decreasing faster in the number of basis functions than the variance is increasing compared to $f_1$. The uncovered and described convex behaviour of the MSPE also might partly attributed by the bias-variance tradeoff. This could not be observed for the FPCR where no clear relationship between the basis functions and the number of FPC was observed. An hypothesis for this would be that the results for the FPCR are mostly driven by the selected FPC´s. To examine this hypothesis, additional simulations were conducted with a large truncation parameter $L$ for $n_{FPC} \in \{2, 3, 4 \}$, which seem to support this claim (LINK TO APPENDIX).

@@

	\section{Application}\label{Application}
		The application uses the methods and insights from the previous sections to predict the octane ratings of the introduced gasoline dataset.
		Although the simulation study granted valuable insights in the different methods in four different settings, it is not enough to determine the method and choice of basis of the application, since there is too much uncertainty involved. To point out some sources of uncertainty: First, opposing to the simulation setup, we do not know the true coefficient function. Visual inspection fuels the hypothesis that the estimated coefficient functions for $NIR$ look closer to $f_2$ than to $f_1$ but the insights from two functions are not enough to draw any conclusion. Second, we have no information about the signal-to-noise ratios of the measured octane numbers. Third, we made assumptions about the distribution of $\xi$ that are not relatable to this real-life application where we not know this distribution. 
		Therefore, we will run all specification again for the gasoline dataset and use the results of the simulation study towards the reading of the results. The application is designed similar to the simulation study: The 60 spectra of the gasoline dataset will be used to regress them on the reported octane numbers and evaluate the results as prediction MSE using 12 fold cross-validation with 5 elements per fold. In total, we conducted 1000 repetitions for each setting.

	\subsection{Interpretation of Results}
		\subsubsection{Basis Expansion Regression}
		\paragraph{Monomial Basis} 
		The cross-validated MSPE selects 5 basis functions, as three out of the four setups in the simulation study. However, we must exercise caution since the results from $L$=6 onwards appear to display signs of numerical instability.

		\paragraph{B-Spline Basis}
		The lowest MSPE is reported for 10 basis functions, most similar to $f_2,Y_1$. Although no convex behaviour can be observed, as for $f_2,Y_1$ the MSPE stays relatively small from 8 basis functions onwards.

		\paragraph{Fourier Basis}
		\subsubsection{Functional Principal Component Regression}
		As for the simulation study, the

@@

	\begin{figure}[H]
		\centering
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/basis_expansion_1_1.pdf}
			\caption{Basis Expansion Regression - $f_1, Y_1$}
		\end{minipage}%
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/basis_expansion_1_2.pdf}
			\caption{Basis Expansion Regression - $f_1, Y_2$}
		\end{minipage}
	\end{figure}

	\begin{figure}[H]
		\centering
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/basis_expansion_2_1.pdf}
			\caption{Basis Expansion Regression - $f_2, Y_1$}
		\end{minipage}%
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/basis_expansion_2_2.pdf}
			\caption{Basis Expansion Regression - $f_2, Y_2$}
		\end{minipage}
	\end{figure}

	\begin{figure}[H]
		\centering
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm2_1_1.pdf}
			\caption{FPC Regression, 2 harmonics - $f_1, Y_1$}
		\end{minipage}%
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm2_1_2.pdf}
			\caption{FPC Regression, 2 harmonics - $f_1, Y_2$}
		\end{minipage}
	\end{figure}

	\begin{figure}[H]
		\centering
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm2_2_1.pdf}
			\caption{FPC Regression, 2 harmonics - $f_2, Y_1$}
		\end{minipage}%
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm2_2_2.pdf}
			\caption{FPC Regression, 2 harmonics - $f_2, Y_2$}
		\end{minipage}
	\end{figure}

	\begin{figure}[H]
		\centering
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm3_1_1.pdf}
			\caption{FPC Regression, 3 harmonics - $f_1, Y_1$}
		\end{minipage}%
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm3_1_2.pdf}
			\caption{FPC Regression, 3 harmonics - $f_1, Y_2$}
		\end{minipage}
	\end{figure}

	\begin{figure}[H]
		\centering
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm3_2_1.pdf}
			\caption{FPC Regression, 3 harmonics - $f_2, Y_1$}
		\end{minipage}%
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm3_2_2.pdf}
			\caption{FPC Regression, 3 harmonics - $f_2, Y_2$}
		\end{minipage}
	\end{figure}

	\begin{figure}[H]
		\centering
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm4_1_1.pdf}
			\caption{FPC Regression, 4 harmonics - $f_1, Y_1$}
		\end{minipage}%
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm4_1_2.pdf}
			\caption{FPC Regression, 4 harmonics - $f_1, Y_2$}
		\end{minipage}
	\end{figure}

	\begin{figure}[H]
		\centering
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm4_2_1.pdf}
			\caption{FPC Regression, 4 harmonics - $f_2, Y_1$}
		\end{minipage}%
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm4_2_2.pdf}
			\caption{FPC Regression, 4 harmonics - $f_2, Y_2$}
		\end{minipage}
	\end{figure}

@@

	\subsection{Application - Coefficient Function Estimates}
	\begin{figure}[H]
		\centering
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Appl\_Curve\_Estimates/appl\_basis\_expansion.pdf}
			\caption{Basis Expansion Regression}
		\end{minipage}%
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Appl\_Curve\_Estimates/fpcr\_nharm2.pdf}
			\caption{2 Functional Principal Components}
		\end{minipage}
	\end{figure}

	\begin{figure}[H]
		\centering
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Appl\_Curve\_Estimates/fpcr\_nharm3.pdf}
			\caption{3 Functional Principal Components}
		\end{minipage}%
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Appl\_Curve\_Estimates/fpcr\_nharm4.pdf}
			\caption{4 Functional Principal Components}
		\end{minipage}
	\end{figure}

>>>>

	\subsection{Results}	
	The discussed results and figures of $\hat{\beta}(t)$ for the simulation can be found in the appendix. 
	\subsubsection{Basis Expansion Regression}
	The following results origin from the \hyperref[basis_exp_transf]{Estimation using Basis-Representation}, in which we transform the smooth curves to perform FLR. Examining the results, it appears that the cross-validated MSPE inherets a convex nature in the increasing basis functions.

	\paragraph{Monomial Basis}
	Due to the in the number of basis functions increasing collinearity of these basis functions, simulations were conducted up until the sixth monomial basis, which already shows signs of numerical instability. For reasons outlined in {\color{green} Link chapter}, they seem suited for $f_1$. The monomial basis shows a better performance than B-splines for this coefficient function. A hypothesis for this could be that $f_1$ is an entire function, which can be well approximated with a power series. In case of $f_2$, this basis shows the weakest performance out of all basis, which is visible in \hyperref[basis_expansion_2_1]{figure 9} and \hyperref[basis_expansion_2_2]{10}, where it seems like $\hat{\beta}(t)$ is not changing in the amount of noise and shows exaggerated behaviour at the boundaries. This weakness is especially pronounced in the MSPE for $f_2,Y_1$. For $f_1$, the simulation selects 5(3) and for $f_2$ 5(5) monomial basis functions for the high(low) signal-to-noise ratios. 
	\vspace{-0.2cm}

	\paragraph{B-spline Basis}
	Simulations with B-spline basis functions were possible from 4 to 18, since from 18 onwards the simulations were running into collinearity problems.
	Function $f_1$ requires only 5(4) B-spline basis functions, for the high(low) signal-to-noise ratio to obtain the best fit for the B-spline basis, which performs the worst for $f_1$. An explanation might be its exaggerated behaviour at the boundaries and the exaggeration of the peculiarities of $f_1$ (\hyperref[basis_expansion_1_1]{ADD} and \hyperref[basis_expansion_1_2]{ADD}), which is especially pronounced for the higher noise responses. For $f_2$, 11(6) B-spline basis functions are chosen for the high(low) signal-to-noise ratios. For $f_2$, the B-spline basis outperforms the monomial basis but comes second to the Fourier basis. While the basis seems to recognize the peculiarities in $f_2,Y_1$, it seems to struggle with it for the noisy responses in $f_2,Y_2$ ((\hyperref[basis_expansion_2_1]{ADD} and \hyperref[basis_expansion_2_2]{ADD})).
	\vspace{-0.2cm}

	\paragraph{Fourier Basis}
	For $f_1$, the simulation chooses a smaller number of Fourier basis functions, 5(3) and a higher number for $f_2$, 9(7) for the setup with the high(low) signal-to-noise ratio. With the low signal-to-noise ratio in the responses, the simulation chooses a smaller number of basis functions, which could be to prevent fitting this scalar noise into $\hat{\beta}(t)$. The Fourier basis functions perform the best for each setup for the basis expansion regression. Several reasons could contribute to this: First, especially $f_1$ shows similar curvature order across the domain while the curvature of $f_2$ does at least not display any erratic jumps. Second, both functions feature periodic behavior. Third, $f_2$ does have the same value at the start- and the end of the interval.	\\

	\subsubsection{Functional Principal Component Regression}
		The model which is used for the FPCR is described in \hyperref[fpc_exp_transf]{Estimation using Functional Principal Components}. Additionally to the selection of the truncation parameter $L$, the choice of the number of FPC's adds to the complexity of the model since the approximated eigenvalues and -functions from the decomposition are influenced by the choice of $L$ that was used to approximate the function. But since the FPCR is ultimately estimated with a linear model with the FPC's as regressors, the relevant degrees of freedom in the estimation of the ultimate model are not affected by $K$, but only by the number of FPC's $n_{FPC} \in \{2, 3, 4 \}$. As will be described, it seems that neither a convex behavior of the MSPE, nor a clear relationship can be observed between the increasing number of basis function and the number of FPC's. This might be since the dependency (FPCA is performed on the smoothed curves) is to complex to draw conclusions from this simulation study, therefore we will limit ourself to a brief description, The results indicate that the FPCR in this simulation seems to not take into account the differing signal-to-noise ratios of the responses since the FPC's, which affect the relevant degrees of freedom, are calculated solely from the smoothed curves, not considering the noise in the responses at all.

	\paragraph{Monomial Basis}
	For $f_1$, the cross-validated MSPE is decreasing in the increasing number of FPC's and chosen basis functions for both the high, and the low signal-to-noise ratio (4,5,6 basis functions for $n_{FPC} \in \{2, 3, 4 \}$). In  $f_2$ we also observe a decreasing MSPE in the number of FPC, but no clear relationship for the choosen basis functions. The monomial basis shows the weakest performance for all three basis functions in each setting.
	\vspace{-0.2cm}

	\paragraph{B-spline Basis}
	For $f_1,Y_1$, the MSPE suggests a better model with a higher number of FPC's. While the number of basis functions stays at five for $n_{FPC} = 2,3$, it increases to 6 basis functions for $n_{FPC} = 4$. In $f_1,Y_2$, the cross-validated MSPE is only slightly affected by $n_{FPC}$, but lowest for $n_{FPC}$ = 3, indicating the possibility of over-fitting for $n_{FPC}$ = 4. Similar to the two setups with $f_1$, the cross-validated number of basis functions for $f_2$ is increasing in the number of FPC's (4,6,23 for $n_{FPC} \in \{2, 3, 4 \}$)
	\vspace{-0.2cm}

	\paragraph{Fourier Basis}
	In $f_1,Y_1$, the MSPE is decreasing in $n_{FPC}$ while the results in $f_1,Y_2$ might indicate overfitting when using four FPC's. $f_2,Y_1$ displays the greatest relative decline of MSE in the increasing number of FPC's, but in absolute values, therefore acknowledging the higher noise responses for $f_2,Y2$, the decline of MSPE is similar to the decline observed for $f_2,Y_2$. Both configurations of $f_2$ are using 5,15,7 basis functions for $n_{FPC} \in \{2, 3, 4 \}$.
	\vspace{-0.2cm}

	\subsubsection{Interpretation and Relevance for Application}
	A possible explanation applicable for the setups performing Basis Expansion Regression might be the effect of the Bias-Variance tradeoff and the following hypothesis: For $f_1$ it might be that little bias is introduced when choosing a small number of basis functions. For $f_2$, a higher number of basis functions seems appropriate, resulting from the inherent peculiarities of $f_2$. This results in higher numbers of basis functions since the amount of bias is decreasing faster in the number of basis functions than the variance is increasing compared to $f_1$. The uncovered and described convex behaviour of the MSPE also might partly attributed by the bias-variance tradeoff. This convex behavior was not observed for the FPCR where no clear relationship between the basis functions and the number of FPC could be uncovered. An hypothesis for this is that the dependency between the truncation $L$ and the FPC's, which are calculated from $L$-truncated smoothed curves, is to complex to capture here. Following this, it appears that the results for the FPCR are mostly driven by the selected FPC´s and less by the choice of basis. To examine this hypothesis, additional simulations were conducted with a large truncation parameter $L \in \{50, 70\}$ for $n_{FPC} \in \{2, \dots, 7 \}$, which seem to support this claim (LINK TO APPENDIX).

@@

	\section{Application}\label{Application}
		The application uses the methods and insights from the previous sections to predict the octane ratings of the introduced gasoline dataset.
		Although the simulation study granted valuable insights in the different methods in four different settings, it is not enough to determine the method and choice of basis of the application, since there is too much uncertainty involved. To point out some sources of uncertainty: First, opposing to the simulation setup, we do not know the true coefficient function. Visual inspection fuels the hypothesis that the estimated coefficient functions for $NIR$ look closer to $f_2$ than to $f_1$ but the insights from two functions are not sufficient to draw any conclusion. Second, we have no information about the signal-to-noise ratios of the measured octane numbers. Third, to generate similar curves, we made assumptions about the distribution of $\mathring{\xi}$ that are not relatable to this real-life application where we not know this distribution. 
		Therefore, we will run all specification again for the gasoline dataset and use the results of the simulation study towards the reading of the results. The application is designed similar to the simulation study: The 60 spectra of the gasoline dataset will be used to regress them on the reported octane numbers and evaluate the results as prediction MSE using 12 fold cross-validation with 5 elements per fold. In total, we conducted 1000 repetitions for each setting.

	\subsection{Interpretation of Results}
		\subsubsection{Basis Expansion Regression}
		\paragraph{Monomial Basis} 
		The cross-validated MSPE selects 5 basis functions for the monomial basis, as three out of the four setups in the simulation study. For B-Splines, the cross-validation selects 10 basis functions and 9 basis functions for the fourier basis. Comparing the estimates in \hyperref[basis_expansion_estimate_appl]{ADD}, apart from the boundaries, B-spline and Fourier basis show similar behavior, opposing to the monomial estimate which might be attributed by the lower basis functions. However, we must exercise caution since from $L$=6 onwards, we were not able to calculate stable results for the monomial basis. Especially at the lower boundary, the monomial basis shows a strong exaggerated bahavior. The MSPE for B-splines (0.04574) and Fourier (0.04808) are similar while it is clearly knocked for the monomial basis (0.24181) by a factor of 5. In contrast to our hypothesis from the simulation study in which we partly attributed the weaker performance of the B-splines to its attributes at the boundaries, it manages to outperform the fourier basis. It is worthy to note that the reported MSPE for the B-spline and Fourier basis are close to the errors reported in the simulation study for the setup $f_2,Y_1$, which might be caused by a similar high signal-to-noise ratio of the octane numbers, but also other factors should be considered.

		\subsubsection{Functional Principal Component Regression}
		As for the simulation study, the interpretation of the results with respect to the choosen basis is difficult. Referring to the plotted estimates $\hat{\beta}(t)$ in \hyperref[FPCR2_estimate_appl]{ADD}, \hyperref[FPCR3_estimate_appl]{ADD} and \hyperref[FPCR4_estimate_appl]{ADD}, it appears that the higher $n_{FPC}$ is, the more similar behaviour of the estimate $\hat{\beta}(t)$ can be observed. Opposing to the simulation study, the number of basis functions is steadily increasing for the monomial basis. The bevahiour for the B-spline basis is similar to the one reported in the simulation study (basis functions increasing in $n_{FPC}$). In contrast to the simulation study, no evidence of overfitting was found for any of the three bases.

@@

	\begin{figure}[H]
		\centering
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/basis_expansion_1_1.pdf}
			\caption{Basis Expansion Regression - $f_1, Y_1$}
			\label{basis_expansion_1_1}
		\end{minipage}%
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/basis_expansion_1_2.pdf}
			\caption{Basis Expansion Regression - $f_1, Y_2$}
			\label{basis_expansion_1_2}
		\end{minipage}
	\end{figure}

	\begin{figure}[H]
		\centering
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/basis_expansion_2_1.pdf}
			\caption{Basis Expansion Regression - $f_2, Y_1$}
			\label{basis_expansion_2_1}
		\end{minipage}%
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/basis_expansion_2_2.pdf}
			\caption{Basis Expansion Regression - $f_2, Y_2$}
			\label{basis_expansion_2_2}
		\end{minipage}
	\end{figure}

	\begin{figure}[H]
		\centering
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm2_1_1.pdf}
			\caption{FPC Regression, 2 harmonics - $f_1, Y_1$}
			\label{fpcr_nharm2_1_1}
		\end{minipage}%
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm2_1_2.pdf}
			\caption{FPC Regression, 2 harmonics - $f_1, Y_2$}
			\label{fpcr_nharm2_1_2}

		\end{minipage}
	\end{figure}

	\begin{figure}[H]
		\centering
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm2_2_1.pdf}
			\caption{FPC Regression, 2 harmonics - $f_2, Y_1$}
			\label{fpcr_nharm2_2_1}
		\end{minipage}%
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm2_2_2.pdf}
			\caption{FPC Regression, 2 harmonics - $f_2, Y_2$}
			\label{fpcr_nharm2_2_2}
		\end{minipage}
	\end{figure}

	\begin{figure}[H]
		\centering
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm3_1_1.pdf}
			\caption{FPC Regression, 3 harmonics - $f_1, Y_1$}
			\label{fpcr_nharm3_1_1}
		\end{minipage}%
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm3_1_2.pdf}
			\caption{FPC Regression, 3 harmonics - $f_1, Y_2$}
			\label{fpcr_nharm3_1_2}
		\end{minipage}
	\end{figure}

	\begin{figure}[H]
		\centering
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm3_2_1.pdf}
			\caption{FPC Regression, 3 harmonics - $f_2, Y_1$}
			\label{fpcr_nharm3_2_1}
		\end{minipage}%
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm3_2_2.pdf}
			\caption{FPC Regression, 3 harmonics - $f_2, Y_2$}
			\label{fpcr_nharm3_2_2}
		\end{minipage}
	\end{figure}

	\begin{figure}[H]
		\centering
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm4_1_1.pdf}
			\caption{FPC Regression, 4 harmonics - $f_1, Y_1$}
			\label{fpcr_nharm4_1_1}
		\end{minipage}%
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm4_1_2.pdf}
			\caption{FPC Regression, 4 harmonics - $f_1, Y_2$}
			\label{fpcr_nharm4_1_2}
		\end{minipage}
	\end{figure}

	\begin{figure}[H]
		\centering
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm4_2_1.pdf}
			\caption{FPC Regression, 4 harmonics - $f_2, Y_1$}
			\label{fpcr_nharm4_2_1}
		\end{minipage}%
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Curve\_Estimates/fpcr_nharm4_2_2.pdf}
			\caption{FPC Regression, 4 harmonics - $f_2, Y_2$}
			\label{fpcr_nharm4_2_2}
		\end{minipage}
	\end{figure}

@@

	\subsection{Application - Coefficient Function Estimates}
	\begin{figure}[H]
		\centering
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Appl\_Curve\_Estimates/appl\_basis\_expansion.pdf}
			\caption{Basis Expansion Regression}
			\label{basis_expansion_estimate_appl}
		\end{minipage}%
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Appl\_Curve\_Estimates/fpcr\_nharm2.pdf}
			\caption{2 Functional Principal Components}
			\label{FPCR2_estimate_appl}			
		\end{minipage}
	\end{figure}

	\begin{figure}[H]
		\centering
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Appl\_Curve\_Estimates/fpcr\_nharm3.pdf}
			\caption{3 Functional Principal Components}
			\label{FPCR3_estimate_appl}	
		\end{minipage}%
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Appl\_Curve\_Estimates/fpcr\_nharm4.pdf}
			\caption{4 Functional Principal Components}
			\label{FPCR4_estimate_appl}	
		\end{minipage}
	\end{figure}
